### 2016-04-08 ms/ms_probaweb.tex
Ben edits

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$,  Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\

@@

3: \\

@@

There are multiple causes of spatial turnover in community composition. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004}. Stochasticity plays an additional role,
either colonization and extinction events \citep{Hanski1999} are inherently
unpredictable, or because of strong non-linear feedbacks in community dynamics generating alternative
transients and equilibria \citep{Chase2007, Vellend2014}. Analyses of
community turnover are usually performed with data represented in a table with
rows corresponding to sites (or measurements) and columns to species. Metrics
of beta diversity quantify the variance of this community data
\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
among communities, such as the Jaccard or Bray–Curtis indices. A more recent
approach decomposes the total variation of the community data into species and
site contributions to beta diversity \citep{Legendre2013}. Even though these
methods compare whole lists of species among sites or measurements, they
remain fundamentally ’species-based’, since they report the variation within
columns. None of them explicitly considers the variation of associations
(i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).

@@

A more integrative description of the niche is key to understand spatial and
temporal turnover in community structure. Despite several attempts to update
the concept of the ecological niche, ecologists have not moved far past the
``n-dimensional hypervolume'' defined by Hutchinson. Despite its intuitive
interpretation and easy translation into species distribution models
\citep{Boulangeat2012, Blonder2014}, the concept has been frequently
criticized \citep{Hardin1960, Peters1991, Silvertown2004}, and several
attempts have been made to expand and reinforce it \citep{Pulliam2000,
Chase2003, Soberon2007, Holt2009, McInerny2012b}.

@@

These perspectives are rather orthogonal to each other, which has resulted in
considerable confusion in the literature \citep{McInerny2012a}.
\citealt{Chase2003} attempted to reconcile with the following definition:
``[The niche is] the joint description of the environmental conditions that
allow a species to satisfy its minimum requirements so that the birth rate of
a local population is equal to or greater than its death rate along with the
set of per capita effects of that species on these environmental conditions''.
Their representation merges zero-net growth isoclines delimiting the
Grinnellian niche (when does the population persists) with impact vectors delimiting
the Eltonian niche (what is the per-capita impact). While this representation
has been very influential in local-scale community ecology (the resource-ratio
theory of coexistence, \citealt{Tilman1982}), it remains impractical at larger
spatial scales because of the difficulties to measure it. The absence of any
mathematical representation of the niche that could easily be fitted to
ecological data may explain why biogeographers are still struggling to develop
species distribution models that also consider ecological interactions.

We propose to integrate the two perspectives of the niche with a visual
representation of both components (Fig. 2). The underlying rationale is that, in
addition to the environmental constraints on demographic performance, any
organism requires resources to sustain its metabolic demands and reproduction.
Abiotic environmental axes are any non-consumable factors affecting the
demographic performance of an organism. Alternatively, the resource axes are
traits of the resources that allow interactions with the consumer. The niche
should therefore be viewed as the set of abiotic environmental factors (the
Grinnellian component) along with the set of traits (the Eltonian component)
that allow a population to establish and to persist at a location. Accordingly,
each species can be characterized by an optimal position in both the
environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
then the hypervolume where interactions can occur and sustain a population.
This approach radically changes the representation of the niche, putting the
distributions and ecological interactions of species in the same formalism.
The limits of the niche axes could be independent of each other (as in the
example of Fig. 2), or alternatively interact. For instance, the optimal
prey size for predatory fishes could decline with increasing temperature
\citep{Lelong2015}, which would make diet boundaries functions of the
environment. The other way around, we could also consider that the growth rate
of the predator changes with the size of its prey items, thereby altering the
environmental boundaries.

@@

There are also variants of the metaweb. First, most documented metawebs have
thus far considered ecological interactions to be deterministic, not
probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to interact
whenever they are found together in a location, independent of their
local abundance and the local environment. In other words, $P(L_{ijy}|X_{ijy}=1) = 1$
and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might be a reasonable
approximation if the scale of sampling and inference is so large that the
probability of observing at least one interaction converges to unity and the
only variation in the networks considered arises from species distributions.

@@

We now turn to an illustration of the framework with the analysis of an
empirical dataset of host–parasite networks sampled throughout the south–north
environmental gradient in continental Europe. The focal system consists of local food webs
of willows (genus Salix), their galling insects, and the parasitoids of
these gallers. Targeting this system, we ask: i) how much does network
structure vary across the gradient, and ii) what is the primary driver of
network turnover across the gradient?

@@

\textbf{Visual representation of the integrated niche}. In biogeography, the
niche is considered the set of environmental conditions where the intrinsic
growth rate $r$ is positive \citep{Holt2009}. The horizontal axis represents an
environmental gradient impacting the growth of the focal species (in red). The
location of each species along this gradient represents their optimum, and the
vertical dotted lines represent the limits of the Grinnellian niche of the
focal species. In food web ecology, the Eltonian niche represents the location
of a species in the food web, as determined by its niche position ($n$) and its
niche optimum ($c$). The vertical axis represents a niche gradient, presumably a
trait such as body size. The location of each species along this gradient
represents their niche position. The focal species will feed on preys having
niche locations within a given interval around the optimum, represented by the
horizontal lines. The integrated Grinnellian and Eltonian niche corresponds to
the square in the middle where an interaction is possible. According to our
probabilistic framework, the central square represents the area where the
joint probability of observing interactions and co-occurrence is positive.

>>>>

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$,  Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\

@@

3: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\

@@

There are multiple causes of spatial turnover in community composition. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004}. Stochasticity plays an additional role,
either colonization and extinction events \citep{Hanski1999} are inherently
unpredictable, or because of strong non-linear feedbacks in community dynamics
generating alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Analyses of community turnover are usually performed with data
represented in a table with rows corresponding to sites (or measurements) and
columns to species. Metrics of beta diversity quantify the variance of this
community data \citep{Legendre2005}. Traditional approaches rely on measures
of dissimilarity among communities, such as the Jaccard or Bray–Curtis
indices. A more recent approach decomposes the total variation of the
community data into species and site contributions to beta diversity
\citep{Legendre2013}, and further partition into dissimilarity due to changes
in species richness and those due to actual species turnover \citep{Baselga2010;
Carvalho et al. 2012}. Even though these methods compare whole lists of
species among sites or measurements, they remain fundamentally ’species-
based’, since they report the variation within columns. None of them
explicitly considers the variation of associations (i.e., of pairs or higher-
order motifs – \citealt{Stouffer2007}).

@@

A more integrative description of the niche is key to understand spatial and
temporal turnover in community structure. Despite several attempts to update
the concept of the ecological niche, ecologists have not moved far past the
``n-dimensional hypervolume'' defined by Hutchinson. Despite its intuitive
interpretation and easy translation into species distribution models
\citep{Boulangeat2012, Blonder2014}, the concept has been frequently
criticized \citep{Hardin1960, Peters1991, Silvertown2004}, and several
attempts have been made to expand and improve it \citep{Pulliam2000,
Chase2003, Soberon2007, Holt2009, McInerny2012b}.

@@

These perspectives are rather orthogonal to each other, which has resulted in
considerable confusion in the literature \citep{McInerny2012a}.
\citealt{Chase2003} attempted to reconcile with the following definition:
``[The niche is] the joint description of the environmental conditions that
allow a species to satisfy its minimum requirements so that the birth rate of
a local population is equal to or greater than its death rate along with the
set of per capita effects of that species on these environmental conditions''.
Their representation merges zero-net growth isoclines delimiting the
Grinnellian niche (when does the population persists) with impact vectors delimiting
the Eltonian niche (what is the per-capita impact). While this representation
has been very influential in local-scale community ecology (the resource-ratio
theory of coexistence, \citealt{Tilman1982}), it remains impractical at larger
spatial scales because of the difficulties in measuring it. The absence of any
mathematical representation of the niche that could easily be fitted to
ecological data may explain why biogeographers are still struggling to develop
species distribution models that also consider ecological interactions.

We propose to integrate the two perspectives of the niche with a visual
representation of both components (Fig. 2). The underlying rationale is that, in
addition to the environmental constraints on demographic performance, any
organism requires resources to sustain its metabolic demands and reproduction.
Abiotic environmental axes are any non-consumable factors affecting the
demographic performance of an organism. Alternatively, the resource axes are
traits of the resources that allow interactions with the consumer. The niche
should therefore be viewed as the set of abiotic environmental factors (the
Grinnellian component) along with the set of traits (the Eltonian component)
that allow a population to establish and to persist at a location. Accordingly,
each species can be characterized by an optimal position in both the
environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
then the hypervolume where interactions can occur and sustain a population.
This approach radically changes the representation of the niche, putting the
distributions and ecological interactions of species in the same formalism.

The limits of the niche axes could be independent of each other (as in the
example in Fig. 2), or  they could interact. For instance, the optimal
prey size for predatory fishes could decline with increasing temperature
\citep{Lelong2015}, which would make diet boundaries functions of the
environment. Alternatively, we could also consider that the growth rate
of the predator changes with the size of its prey items, thereby altering the
environmental boundaries.

@@

There are also variants of the metaweb. First, most documented metawebs have
thus far considered ecological interactions to be deterministic, not
probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to
interact whenever they are found together in a location, independent of their
local abundance and the local environment. In other words,
$P(L_{ijy}|X_{ijy}=1) = 1$ and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might
be a reasonable approximation if the scale of sampling and inference is so
large that the probability of observing at least one interaction converges to
unity In this cenario, network variation solely arises from species
distributions.

@@

We now turn to an illustration of our framework with the analysis of an
empirical dataset of host–parasite networks sampled throughout the south–north
environmental gradient in continental Europe. The focal system consists of
local food webs of willows (genus Salix), their galling insects, and the
parasitoids of these gallers. Targeting this system, we ask: i) how much does
network structure vary across the gradient, and ii) what is the primary driver
of network turnover across the gradient?

@@

\textbf{Visual representation of the integrated niche}. In biogeography, the
niche is considered the set of environmental conditions where the intrinsic
growth rate $r$ is positive \citep{Holt2009}. The horizontal axis represents
an environmental gradient impacting the growth of the focal species (in red).
The location of each species along this gradient represents their optimum, and
the vertical dotted lines represent the limits of the Grinnellian niche of the
focal species. In food web ecology, the Eltonian niche represents the location
of a species in the food web, as determined by its niche position ($n$) and
its niche optimum ($c$). The vertical axis represents a niche gradient,
presumably a trait such as body size. The location of each species along this
gradient represents their niche position. The focal species will feed on prey
species  niche locations within a given interval around the optimum,
represented by the horizontal lines. The integrated Grinnellian and Eltonian
niche corresponds to the square in the middle where an interaction is possible
owing to a match of traits and spatial distribution. According to our
probabilistic framework, the central square represents the area where the
joint probability of observing interactions and co-occurrence is positive.
